Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{ Funded by DARPA Cyber Assured Systems Engineering (CASE) contract HR00111890001. }

### 2021-05-06 paper/example.tex
Fix typo and update ML

\newsavebox{\cml}
\begin{lrbox}{\cml}
\begin{lstlisting}[style=myML]
fun filter_step () =
let val () = Utils.clear_buf buffer
    val () = API.callFFI "get_input" "" buffer
    val string = Utils.buf2string buffer
in
    if WELL_FORMED_AUTOMATION_RESPONSE string
    then
        let val string = Word8Array.substring buffer 1
                         (Word8Array.length buffer - 1)
        in API.callFFI "put_output" string Utils.emptybuf
        end
    else print"Filter rejects message.\n"
end
\end{lstlisting}
\end{lrbox}

>>>>

\newsavebox{\cml}
\begin{lrbox}{\cml}
\begin{lstlisting}[style=myML]
fun filter_step () =
let val () = Utils.clear_buf buffer
    val () = API.callFFI "get_input" "" buffer
    val string = Utils.buf2string buffer
    val policy = WELL_FORMED_AUTOMATION_RESPONSE string 
in
    if policy
    then
        let val string = Word8Array.substring buffer 1
                         (Word8Array.length buffer - 1)
        in API.callFFI "put_output" string Utils.emptybuf
        end
    else print"Filter rejects message.\n"
end
\end{lstlisting}
\end{lrbox}

### 2021-05-06 paper/system.tex
Fix typo and update ML

\begin{figure}
  \[
    \begin{array}{rcl}
      \mathit{c}    & = & \konst{input}\ [(f : \tau)\ldots] \\
                    &   & \konst{output}\ [(f : \tau)\ldots] \\
                    &   & \konst{eq}\; f : \tau := \mathit{exp} \\
                    &   & \konst{guarantees}\ [\mathit{bexp}\ldots]\\

>>>>

\begin{figure}
  \[
    \begin{array}{rcl}
      \mathit{c}    & = & \konst{input}\ [(f : \tau)\ldots] \\
                    &   & \konst{output}\ [(f : \tau)\ldots] \\
                    &   & \konst{eq}\; [(f : \tau := \mathit{exp})\ldots] \\
                    &   & \konst{guarantees}\ [\mathit{bexp}\ldots]\\
